Lambda Calculus through Tropical Mathematics

### 2023-01-10 section2.tex
commit

Since polynomials correspond to linear (hence Lipschitz) functions in tropical mathematics, the reconstruction of the relational semantics over the tropical semi-ring, presented in Section \ref{section3} and Section \ref{section4}, will provide a metric semantics of the differential $\lambda$-calculus, bridging sensitivity and resource analysis. 
In Section \ref{section5} we will suggest potential applications of this approach, relating well-studied applications of program metrics, resource analysis with current uses of tropical mathematics in computer science.  
Finally, in Section \ref{section6} we will show that the connection between the metric and differential analysis of higher-order programs extends well beyond the relational semantics, through a more abstract correspondence between the theory of 
\emph{generalized metric spaces} (in the sense of Lawvere \cite{}) and the theory of modules over the tropical semi-ring.

>>>>

Since polynomials correspond to linear (hence Lipschitz) functions in tropical mathematics, the reconstruction of the relational semantics over the tropical semi-ring, presented in Section \ref{section3} and Section \ref{section4}, will provide a metric semantics of the differential $\lambda$-calculus, bridging sensitivity and resource analysis. 
In Section \ref{section5} we will suggest potential applications of this approach, relating well-studied applications of program metrics, resource analysis with current uses of tropical mathematics in computer science.  
Finally, in Section \ref{section6} we will show that the connection between the metric and differential analysis of higher-order programs extends well beyond the relational semantics, through a more abstract correspondence between  
\emph{generalized metric spaces} (in the sense of Lawvere \cite{}) and modules over the tropical semi-ring.
